---
title: "worms demo"
output: html_notebook
author: Maggie Seida
---

Example, biodiversity assesment: A team of scientists are on an expedition to determine the biodiveristy of Monterey Bay. By scuba diving, taking data from a boat, and conducting tide pool surveys, they identify 500 different species in the bay.  

This is great, but they're running out of funding! Coincidentally, there is a philanthropist in town who loves sea slugs, specifically nudibranchs ("nudi"=naked, "branch"=gills). If the team can show that from the data they've collected so far, 20% of the species are nudies, the philanthropist will donate $500,000 to fund their research.   
  
The problem is, they didn't sort their data as they collected it, so marine birds are mixed with fish which are mixed with sea slugs!


```{r}
#install.packages("worms") #remove #s to run install code
library(worms)

taxon_names <- c( "Pelecanus occidentalis", "Felimare porterae", "Strongylocentrotus purpuratus", "Enhydra lutris", "Flabellinopsis iodinea", "Zalophus californianus", "Patiria miniata", "Stereolepis gigas", "Anarrhichthys ocellatus", "Melibe leonina", "Aplysia californica", "Acmaea mitra", "Lottia pelta") #Here we are listing our unorganized, Monterey marine species, by scientific name
w <- wormsbynames(taxon_names) #verifies all names are correct and up-to-date

```

```{r}
SOS <- wormsbynames(taxon_names, ids = FALSE, match = FALSE, verbose = TRUE,
chunksize = 4, like = "false", marine_only = "true",
sleep_btw_chunks_in_sec = 0.1) #names a data set with marine only species (maybe someone included a terrestrial bird?) and requests species info from WoRMs based on species name
```

```{r}
SOS #let's look at what this gives us
```



```{r}
gastropoda=subset(SOS, class=="Gastropoda")

gastropoda #sea slugs are within the gastropod class, how many gastropods do we have?
```
>Here we can see that 5 of the 13 species are gastropods. But how many are nudibranchs?

```{r}
nudibranchia=subset(gastropoda, order="Nudibranchia")
nudibranchia #let's sort out only the nudibranchs
```
>Here we can see that 3 of the 5 gastropods are nudibranchs!!

Out of our species, 23.1% are nudibranchs!!

Funding received!!!

