---
title: "Esquisse"
author: "Gemma Kirkham"
date: "10/27/2019"
output: github_document
---

First, we want to install and load esquisse into R ready to use. 

```{r}
#install.packages("esquisse")
library(esquisse)
library(tidyverse)
```

We are also going to use the diamonds dataset from the ggplot2 package. Ensure that this is also loaded before continuing. This also allows you to see what kind of data you are handling.

```{r}
#diamonds
#iris
```

Obviously diamonds is a pretty large dataset and it may be hard to recognise what you want to show on a graph and whether you want to select certain parts of the data to use. There are two ways of accessing the esquisse library. We can either use the command below or we go to Addins menu and select 'ggplot2' builder under Esquisse. This will bring up a window where you can select your data.frame and what variables you would like in your plot. It also tells you what type of variables they are.

```{r eval=FALSE}
esquisse::esquisser(diamonds)
esquisse::esquisser(iris)
```
```{r}
ggplot(iris) +
 aes(x = Sepal.Length, colour = Species) +
 geom_density(adjust = 1L, fill = "#0c4c8a") +
 scale_color_hue() +
 theme_minimal()
```


```{r}
diamonds <- diamonds %>% 
 filter(cut %in% "Ideal") %>%
 filter(color %in% c("F", "G", "D")) %>%
 
    filter(clarity %in% c("VVS1", "I1", "IF")) %>%
 filter(depth >= 52L & depth <= 
    79L) %>%
 filter(x >= 2.7 & x <= 10.8)

ggplot(diamonds) +
 aes(x = x, y = price, colour = color) +
 geom_point(size = 1L) +
 scale_color_hue() +
 labs(x = "Length of diamond", y = "Price", title = "Graph", subtitle = "Using esquisse", color = "Colour") +
 theme_minimal()
```
```{r}
diamonds <- diamonds %>%
 filter(cut %in% "Ideal") %>%
 filter(clarity %in% "IF")

ggplot(diamonds) +
 aes(x = carat, y = price, colour = depth, size = color) +
 geom_point() +
 scale_color_gradient() +
 theme_minimal()
```


```{r}
diamonds <- diamonds %>%
 filter(cut %in% "Ideal") %>%
 filter(!(color %in% c("E", "H", "G"))) %>%
 
    filter(clarity %in% c("SI2", "VVS1", "I1", "IF")) %>%
 filter(depth >= 43L & depth <= 
    73L)

ggplot(diamonds) +
 aes(x = x, y = price, colour = color) +
 geom_point(size = 1L) +
 scale_color_brewer(palette = "Set3") +
 labs(x = "Length") +
 theme_minimal()
```

